\input{header.tex}
\usepackage{listings}
\title{YeSr LabRAD}
\begin{document}
\maketitle

\section{Installation}
\subsection{LabRAD Manager}
The labrad \href{https://github.com/labrad/scalabrad}{\underline{manager}} and \href{https://github.com/labrad/scalabrad-web}{\underline{web interface}} can be found on github. We run these along with our database on a dedicated linux box. systemd unit files can be found in our \href{https://github.com/yesrgang/labrad}{\underline{github labrad repository}}.

Each machine needs the following environment variables. LABRADHOST is hostname of machine running the manager. LABRADNODE is the machine's name e.g. ``yesr5". LABRADPASSWORD is a password. LABRAD\_TLS is ``off".

\subsection{pylabrad}
Here is a list of python dependencies. 
\begin{itemize}
    \item required
    \begin{itemize}
        \item python 2.7.11
        \item twisted
        \item pylabrad
    \end{itemize}
    \item generally useful
    \begin{itemize}
        \item numpy 
        \item scipy
        \item matplotlib
        \item pyserial 2.7
        \item pyvisa 1.8
    \end{itemize}
    \item optional
    \begin{itemize}
        \item Opal Kelly Front Panel
        \item python-vxi11
    \end{itemize}
\end{itemize}
These can be installed however you like (pip, virtualenv).

\section{Usage}
\subsection{Simple Connection}
If the labrad manager is running and environment variables are set correctly
\begin{lstlisting}[language=bash]
    >> import labrad
    >> cxn = labrad.connect()
\end{lstlisting}


\end{document}
